### 2016-09-10 appendix.tex
Revision inlcluded
Current Version

\begin{proof}
$\Gamma$ can be formalized using linear algebra:
Let $G_A$ be an aggregated graph, with a $n \times n$ adjacent matrix $J$.
Since a vertex order is a permutation of $J$, the adjacent matrices 
of any reordered graphs can be represented as $PJP^T$
where $P \in \mathbb{P}$ is a $n\times n$ \emph{permutation matrix}~\footnote{an identity matrix with rows shuffled}.
In star partitioning, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
vector with size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orderings, that is

\begin{equation}
\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
\end{equation}

Let $B^*$ be the assignment matrix wrt. the optimal vertex ordering.
Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 
$\Gamma^*=||B^*\vec{b}||_\infty \geq d/2$.
Next, for a vertex ordering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
edges in graph $G$ are independent, then $e_{i,j}$s are independent. 
Let $d_i$ denote the degree of vertex $i$, since a vertex ordering does not
affect the average degree,
then $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$. Therefore, 
entries in $B$ can be written as :

\begin{equation*}
b_{i,j} = \begin{cases}
			e_{i,j}, i>j \\
			0, otherwise
		  \end{cases}  
\end{equation*}

There are two observations. First, since $e_{i,j}$s are independent,
$b_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$s are independent. 
$E[b_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.
As $c_i$ is a sum of $n$ independent 0-1 variables ($b_{i.j}$s). By linearity 
of expectations,
we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} b_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$.
 Let $\mu =E[c_i] = d/2$, 
$t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:

\begin{equation*}
\begin{split}
	Pr(c_i \geq \mu + t) &\leq \exp(\frac{-2t^2}{n}) = \exp(-2\log n) = n^{-2}
\end{split}
\end{equation*}

The first step holds since all $b_{i,j}$ are 0-1 variables. 
Next, the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, the following holds:
\begin{equation*}
\begin{split}
	Pr(\Gamma \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) = n^{-1} = 1/n
\end{split}
\end{equation*}
Substitute back $t$ and $\mu$, we achieve the following concise form:
\begin{equation*}
	Pr(\Gamma \geq (d/2 + \sqrt{n\log n})) \leq 1/n
\end{equation*}
This indicates the probability of $(\Gamma-d/2)$ being no greater than $ O(\sqrt{n\log n})$ is $(1-1/n)$. 
Since $\Gamma^* \geq d/2$, it follows with probability greater than $(1-1/n)$, 
the $\Gamma - \Gamma^*$ is no greater than $O(\sqrt{n\log n})$.
When the aggregated graph is \emph{dense} (i.e., $d\geq \sqrt{12 \log n}$),
the Chernoff Bound can be used to derive a tighter bound of 
$O(\sqrt{\log n}) $ following the similar reasoning.
\end{proof}

>>>>

\begin{proof}
$\Gamma$ can be formalized using linear algebra:
Let $G_A$ be an aggregated graph, with a $n \times n$ adjacent matrix $J$.
Since a vertex order is a permutation of $J$, the adjacent matrices 
of any reordered graphs can be represented as $PJP^T$
where $P \in \mathbb{P}$ is a $n\times n$ \emph{permutation matrix}~\footnote{an identity matrix with rows shuffled}.
In star partitioning, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
vector with size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orderings, that is:
\vspace{-2mm}
\begin{equation}
\vspace{-2mm}
\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
\end{equation}

Let $B^*$ be the assignment matrix wrt. the optimal vertex ordering.
Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 
$\Gamma^*=||B^*\vec{b}||_\infty \geq d/2$.
Next, for a vertex ordering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
edges in graph $G$ are independent, then $e_{i,j}$s are independent. 
Let $d_i$ denote the degree of vertex $i$, since a vertex ordering does not
affect the average degree,
then $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$. Therefore, 
entries in $B$ can be written as :
\vspace{-2mm}
\begin{equation*}
\vspace{-1mm}
b_{i,j} = \begin{cases}
			e_{i,j}, i>j \\
			0, otherwise
		  \end{cases}  
\end{equation*}

There are two observations. First, since $e_{i,j}$s are independent,
$b_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$s are independent. 
$E[b_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.
As $c_i$ is a sum of $n$ independent 0-1 variables ($b_{i.j}$s). By linearity 
of expectations,
we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} b_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$.
 Let $\mu =E[c_i] = d/2$, 
$t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:
\vspace{-2mm}
\begin{equation*}
\vspace{-2mm}
\begin{split}
	Pr(c_i \geq \mu + t) &\leq \exp(\frac{-2t^2}{n}) = \exp(-2\log n) = n^{-2}
\end{split}
\end{equation*}

The first step holds since all $b_{i,j}$ are 0-1 variables. 
Next, the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, the following holds:
\vspace{-2mm}
\begin{equation*}
\vspace{-2mm}
\begin{split}
	Pr(\Gamma \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) = n^{-1} = 1/n
\end{split}
\end{equation*}
Substitute back $t$ and $\mu$, we achieve the following concise form:
\vspace{-2mm}
\begin{equation*}
	Pr(\Gamma \geq (d/2 + \sqrt{n\log n})) \leq 1/n
\end{equation*}
This indicates the probability of $(\Gamma-d/2) \leq O(\sqrt{n\log n})$ is $(1-1/n)$. 
Since $\Gamma^* \geq d/2$, it follows with probability greater than $(1-1/n)$, 
$\Gamma - \Gamma^* \leq O(\sqrt{n\log n})$.
When the aggregated graph is \emph{dense} (i.e., $d\geq \sqrt{12 \log n}$),
the Chernoff Bound can be used to derive a tighter bound of 
$O(\sqrt{\log n}) $ following similar reasoning.
\end{proof}

### 2016-09-10 sec1_introduction.tex
Current Version

A crucial task of data analysis on top of trajectories is 
to discover co-moving objects. A \emph{co-movement} pattern~\cite{li2013managing,zheng2015survey} 
refers to a group of objects traveling together for a certain period of time 
and the group is normally determined by their spatial proximity. 
A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such a basic definition 
and driven by different mining applications, there are \revised{many} variants 
of co-movement patterns that have been developed with additional constraints.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns. The example consists of six trajectories across six snapshots. Objects in spatial clusters are enclosed by dotted circles. $M$ is the minimum cluster cardinality; $K$ denotes the minimum number of snapshots for the occurrence of a spatial cluster; and $L$ denotes the minimum length for local consecutiveness.}
\label{fig:related_work}
\end{figure}

@@

\begin{figure}[h]
\center
\includegraphics[width=0.3\textwidth]{platoon_weakpoint.eps}
\caption{\emph{Loose-connection} anomaly. Even though $\langle o_1, o_2: 1,2,3,102,103,104 \rangle$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart. 
}
\label{fig:platoon_weakpoint}
\end{figure}

\begin{table}[t]
\centering
\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{2cm}|p{2.3cm}|}
\hline 
\textbf{Pattern} & {\textbf{Proximity}} & { \textbf{Consecutive-ness}} & { \textbf{Time  Complexity}}\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk &  global & {$O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
\hline 
convoy~\cite{jeung2008convoy} & density &   global & {$O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
swarm~\cite{li2010swarm} & density  & - & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk &  local & {$O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
\hline 
platoon~\cite{li2015platoon} & density &  local & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
\end{tabular} 
\caption{Constraints and complexities of co-movement patterns. The time complexity indicates the performance wrt.
$|\mathbb{O}|$, $|\mathbb{T}|$ in the worst case, where $|\mathbb{O}|$ is the number of objects, and $|\mathbb{T}|$ is the number of discretized timestamps.}
\label{tbl:existing_co_patterns}
\end{table}

@@

\begin{figure}[h]
	\vspace{-3mm}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{\small Varying No. of objects} 
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{\small Varying No. of timestamps}
    \label{fig:fig2}
    \end{subfigure}
    \vspace{-2mm}
    \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
    is used with upto 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
    \label{fig:related_work_scalability}
\end{figure}

Therefore, we aim to close these two gaps in this paper. 
First, we propose the \emph{general co-movement pattern} (GCMP) which models
various co-moment patterns in a unified way and can avoid 
the \emph{loose-connection} anomaly. In GCMP, we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. 
%\revised{In GCMP, we adopt the concept of \emph{gap parameter $G$}
%in sequential pattern mining field~\cite{srikant1996mining} to constrain the temporal distance between two consecutive %segments.} 
By setting a feasible $G$, the loose-connection anomaly can be effectively controlled. In addition, our GCMP is also general. %and expressive. 
It can be reduced to any of the previous patterns by customizing its parameters.

@@

We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions of
temporal points. 
The results show that both our parallel schemes efficiently support GCMP mining in large datasets.
In particular, with over 170 million trajectory points,
SPARE achieves upto 112 times speedup using 162 cores as compared to the state-of-the-art centralized schemes.
Moreover, SPARE further achieves almost linear scalability with upto 14 times efficiency
as compared to the baseline algorithm.

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining. Section~\ref{sec:definition} defines the problem of general co-movement pattern mining. Section~\ref{sec:trm} provides a baseline solution. An advanced solution named
\emph{Star Partitioning and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}. Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our solutions. Finally, Section~\ref{sec:concl} concludes the paper.

>>>>

A crucial task of data analysis on top of trajectories is 
to discover co-moving objects. A \emph{co-movement} pattern~\cite{li2013managing,zheng2015survey} 
refers to a group of objects traveling together for a certain period of time 
and the group is normally determined by their spatial proximity. 
A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such a basic definition 
and driven by different mining applications, there are many variants 
of co-movement patterns that have been developed with additional constraints.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{related_work.eps}
\vspace{-0.5em}
\caption{Trajectories and co-movement patterns. The example consists of six trajectories across six snapshots. Objects in spatial clusters are enclosed by dotted circles. $M$ is the minimum cluster cardinality; $K$ denotes the minimum number of snapshots for the occurrence of a spatial cluster; and $L$ denotes the minimum length for local consecutiveness.}
\label{fig:related_work}
\end{figure}

@@

\begin{figure}[h]
\center
\includegraphics[width=0.3\textwidth]{platoon_weakpoint.eps}
   \vspace{-0.5em}
\caption{\emph{Loose-connection} anomaly. Even though $\langle o_1, o_2: 1,2,3,102,103,104 \rangle$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart. 
}
\label{fig:platoon_weakpoint}
\end{figure}

\begin{table}[t]
\centering
\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{2cm}|p{2.3cm}|}
\hline 
\textbf{Pattern} & {\textbf{Proximity}} & { \textbf{Consecutive-ness}} & { \textbf{Time  Complexity}}\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk &  global & {$O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
\hline 
convoy~\cite{jeung2008convoy} & density &   global & {$O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
swarm~\cite{li2010swarm} & density  & - & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk &  local & {$O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
\hline 
platoon~\cite{li2015platoon} & density &  local & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
\end{tabular} 
\vspace{-0.5em}
\caption{Constraints and complexities of co-movement patterns. The time complexity indicates the performance wrt.
$|\mathbb{O}|$, $|\mathbb{T}|$ in the worst case, where $|\mathbb{O}|$ is the number of objects, and $|\mathbb{T}|$ is the number of discretized timestamps.}
\label{tbl:existing_co_patterns}
\end{table}

@@

\begin{figure}[h]
	\vspace{-3mm}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
            \vspace{-1.5em}
		\subcaption{ Varying No. of objects} 
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
            \vspace{-1.5em}
         \subcaption{ Varying No. of timestamps}
    \label{fig:fig2}
    \end{subfigure}
    \vspace{-0.5em}
    \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
    is used with upto 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
    \label{fig:related_work_scalability}
\end{figure}

Therefore, in this paper, our contributions are to closing these two gaps.
%In this paper, our contribution is towards closing these two gaps.
First, we propose the \emph{general co-movement pattern} (GCMP) which models
various co-moment patterns in a unified way and can avoid 
the \emph{loose-connection} anomaly. In GCMP, we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. 
%\revised{In GCMP, we adopt the concept of \emph{gap parameter $G$}
%in sequential pattern mining field~\cite{srikant1996mining} to constrain the temporal distance between two consecutive %segments.} 
By setting a feasible $G$, the loose-connection anomaly can be effectively controlled. In addition, our GCMP is also general. %and expressive. 
It can be reduced to any of the previous pattern by customizing its parameters.

@@

We conduct a set of extensive experiments on three large-scale real datasets with hundreds of millions of
temporal points. 
The results show that both our parallel schemes efficiently support GCMP mining in large datasets.
In particular, with over 170 million trajectory points,
SPARE achieves upto 112 times speedup using 162 cores as compared to the state-of-the-art centralized schemes.
Moreover, SPARE further achieves almost linear scalability with upto 14 times efficiency
as compared to the baseline algorithm.

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining. Section~\ref{sec:definition} states the problem of general co-movement pattern mining. Section~\ref{sec:trm} provides a baseline solution named \emph{Temporal Replication and Parallel Mining} (TRPM). An advanced solution named
\emph{Star Partitioning and ApRiori Enumerator} (SPARE) is presented in Section~\ref{sec:spm}. Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our solutions. Finally, Section~\ref{sec:concl} concludes the paper.

### 2016-09-10 sec3_definitions.tex
Current Version

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =(1,2,...,N)$ be the discretized temporal dimension. A time sequence $T$ is defined as an ordered subset of $\mathbb{T}$. Given two time sequences $T_1$ and $T_2$, we define \revised{several} commonly-used operators in this paper in Table~\ref{tbl:operators}.

\begin{table}[h]
\vspace{-2mm}
\centering
\begin{tabular}{|c|l|}
\hline 
\textbf{Operator} & \textbf{Definition} \\ 
\hline
$T[i]$ & the $i$-th element in the sequence $T$ \\ 
\hline
$|T|$ & the number of elements in $T$\\
\hline
$\max(T)$ & the maximum element in $T$\\
\hline
$\min(T)$ & the minimum element in $T$\\
\hline
$\range(T)$ & the range of $T$, i.e., $\max(T) - \min(T) +1$\\ 
\hline 
$T[i:j]$ & subsequence of $T$ from $T[i]$ to $T[j]$ (inclusive) \\ 
\hline
$T_1\subseteq T_2$ &  $\forall T_1[x]\in T_1$, we have $T_1[x]\in T_2$. \\\hline
$T_3=T_1\cup T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ or $T_3[x] \in T_2$\\ 
\hline
$T_3=T_1\cap T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ and $T_3[x] \in T_2$\\ 
\hline
\end{tabular}
\caption{Operators on time sequence.} \label{tbl:operators}
\end{table}

\vspace{-3mm}
We say a sequence $T$ is consecutive 
if $\forall i \in (1,...,|T|-1), T[i+1] = T[i] + 1$.  We refer to each consecutive subsequence of $T$ as a \emph{segment}.
It is obvious that any time sequence $T$ can be decomposed into
segments and we say $T$ is \textit{L-consecutive}~\cite{li2015platoon} 
if the length of every segment is no smaller than $L$. As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose connection} anomaly. 
To avoid such an anomaly without losing generality, we introduce a parameter $G$ to control the gaps between
timestamps in a pattern. Formally, a $G$-connected time sequence is defined as follows:

@@

We take $T=(1,2,3,5,6)$ as an example, which can be decomposed into two segments $(1,2,3)$ and $(5,6)$. $T$ is not $3$-consecutive since the length of $(5,6)$ is $2$. Thus, it is safe to say either $T$ is $1$-consecutive or $2$-consecutive. On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring timestamps is $2$. It is worth noting that $T$ is not $1$-connected because the gap between $T[3]$ and $T[4]$ is $2$ (i.e., $5-3=2$).

Given a trajectory database that is discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textbf{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textbf{significance:} $|O| \geq M$; (3) \textbf{duration:} $|T| \geq K$; (4) \textbf{consecutiveness:} $T$ is $L$-consecutive; and (5) \textbf{connection:} $T$ is $G$-connected.
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$. 
%\revised{These parameters have different effects on the number of patterns discovered. Larger $K$, $L$, $M$ 
%put more stringent constraints on patterns such that less patterns could satisfy the requirements. Larger $G$
%relaxes the temporal constraints therefore more patterns could be discovered. Currently, we leave tuning of
%parameters to users to accommodate various application needs.}  
By customizing these parameters, our pattern can 
express other patterns proposed in the literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern. By setting $G=|\mathbb{T}|,L=1$, we reach the \emph{swarm} pattern. By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we result in the \emph{convoy} and \emph{flock} patterns. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
%It is notable that GCMP cannot be modeled by existing patterns. 
\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
\textbf{Pattern} & $M$ & $K$ & $L$ & $G$ & \textbf{Clustering} \\ 
\hline
Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & disk\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & disk \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & density\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & density\\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & density\\  
\hline 
\end{tabular} 
\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value.
% $M$ represents the  \emph{significance} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.
}
\label{tbl:patterns}
\end{table}

\vspace{-2mm}
Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
We currently expose both disk-region based clustering and DBSCAN as options to the users. In summary, the goal of this paper is to present a parallel solution for discovering all the valid GCMPs from large-scale trajectory databases. Before we move on to the algorithmic part, we list the notations that are used in the following sections.

\begin{table}[h]
\centering
\begin{tabular}{|c|l|} 
\hline
\textbf{Symbol} & \textbf{Meaning} \\
\hline
$S_t$ & snapshot of objects at time $t$ \\
\hline
$M$ & significance constraint \\
\hline 
$K$ & duration constraint\\
\hline
$L$ & consecutiveness constraint\\
\hline
$G$ & connection constraint \\
\hline
$P=\langle O:T \rangle$ & pattern with object set $O$, time sequence $T$\\
\hline
%$C_t(o)$ & cluster of object $o$ at time $t$ \\
%\hline 
$S_t$ & set of clusters at snapshot $t$\\
\hline
$\eta$ & replication factor in the TRPM framework\\
\hline 
$\lambda_t$ & partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
\hline
$G_A$ & aggregated graph in SPARE framework\\
\hline
$Sr_i $ &  star partition for object (vertex) $i$ \\
\hline 
$\Gamma$ & size of the largest star partition\\
\hline
\end{tabular} 
\caption{Summary of the use of notations.}
\end{table}

>>>>

\section{Problem Statement}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =(1,2,...,N)$ be the discretized temporal dimension. A time sequence $T$ is defined as an ordered subset of $\mathbb{T}$. Given two time sequences $T_1$ and $T_2$, we define commonly-used operators in this paper in Table~\ref{tbl:operators}.

\begin{table}[h]
\vspace{-2mm}
\centering
\begin{tabular}{|c|p{6.5cm}|}
\hline 
\textbf{Operator} & \textbf{Definition} \\ 
\hline
$T[i]$ & the $i$-th element in the sequence $T$ \\ 
\hline
$|T|$ & the number of elements in $T$\\
\hline
$\max(T)$ & the maximum element in $T$\\
\hline
$\min(T)$ & the minimum element in $T$\\
\hline
$\range(T)$ & the range of $T$, i.e., $\max(T) - \min(T) +1$\\ 
\hline 
$T[i:j]$ & subsequence of $T$ from $T[i]$ to $T[j]$ (inclusive) \\ 
\hline
$T_1\subseteq T_2$ &  $\forall T_1[x]\in T_1$, we have $T_1[x]\in T_2$. \\\hline
$T_3=T_1\cup T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ or $T_3[x] \in T_2$\\ 
\hline
$T_3=T_1\cap T_2$ & $\forall T_3[x]\in T_3$, we have $T_3[x]\in T_1$ and $T_3[x] \in T_2$\\ 
\hline
\end{tabular}
\vspace{-0.5em}
\caption{Operators on time sequence.} \label{tbl:operators}
\end{table}

We say a sequence $T$ is consecutive 
if $\forall i \in (1,...,|T|-1), T[i+1] = T[i] + 1$.  We refer to each consecutive subsequence of $T$ as a \emph{segment}.
It is obvious that any time sequence $T$ can be decomposed into
segments and we say $T$ is \textit{L-consecutive}~\cite{li2015platoon} 
if the length of every segment is no smaller than $L$. As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose connection} anomaly. 
To avoid such an anomaly without losing generality, we introduce a parameter $G$ to control the gaps between
timestamps in a pattern. Formally, a $G$-connected time sequence is defined as follows:

@@

We take $T=(1,2,3,5,6)$ as an example. $T$ can be decomposed into two segments $(1,2,3)$ and $(5,6)$. $T$ is not $3$-consecutive since the length of $(5,6)$ is $2$. But it is safe to say either $T$ is $1$-consecutive or $2$-consecutive. On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring timestamps is $2$. It is worth noting that $T$ is not $1$-connected because the gap between $T[3]$ and $T[4]$ is $2$ (i.e., $5-3=2$).

Given a trajectory database that is discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: (1) \textbf{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; (2) \textbf{significance:} $|O| \geq M$; (3) \textbf{duration:} $|T| \geq K$; (4) \textbf{consecutiveness:} $T$ is $L$-consecutive; and (5) \textbf{connection:} $T$ is $G$-connected.
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$. 
%\revised{These parameters have different effects on the number of patterns discovered. Larger $K$, $L$, $M$ 
%put more stringent constraints on patterns such that less patterns could satisfy the requirements. Larger $G$
%relaxes the temporal constraints therefore more patterns could be discovered. Currently, we leave tuning of
%parameters to users to accommodate various application needs.}  
By customizing these parameters, our pattern can 
express other patterns proposed in the literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern. By setting $G=|\mathbb{T}|,L=1$, we reach the \emph{swarm} pattern. By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we result in the \emph{convoy} and \emph{flock} patterns. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
%It is notable that GCMP cannot be modeled by existing patterns. 
\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
\textbf{Pattern} & $M$ & $K$ & $L$ & $G$ & \textbf{Clustering} \\ 
\hline
Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & disk\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & disk \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & density\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & density\\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & density\\  
\hline 
\end{tabular} 
    \vspace{-0.5em}
\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value.
% $M$ represents the  \emph{significance} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.
}
    \vspace{-0.5em}
\label{tbl:patterns}
\end{table}

Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
We currently expose both disk-region based clustering and DBSCAN as options to the users. In summary, the goal of this paper is to present a parallel solution for discovering all the valid GCMPs from large-scale trajectory databases. Before we move on to the algorithmic part, we list the notations that are used in the following sections.

\begin{table}[h]
\centering
\begin{tabular}{|c|l|} 
\hline
\textbf{Symbol} & \textbf{Meaning} \\
\hline
$S_t$ & snapshot of objects at time $t$ \\
\hline
$M$ & significance constraint \\
\hline 
$K$ & duration constraint\\
\hline
$L$ & consecutiveness constraint\\
\hline
$G$ & connection constraint \\
\hline
$P=\langle O:T \rangle$ & pattern with object set $O$, time sequence $T$\\
\hline
%$C_t(o)$ & cluster of object $o$ at time $t$ \\
%\hline 
$S_t$ & set of clusters at snapshot $t$\\
\hline
$\eta$ & replication factor in the TRPM framework\\
\hline 
$\lambda_t$ & partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
\hline
$G_A$ & aggregated graph in SPARE framework\\
\hline
$Sr_i $ &  star partition for object (vertex) $i$ \\
\hline 
$\Gamma$ & size of the largest star partition\\
\hline
\end{tabular} 
\vspace{-0.5em}
\caption{Summary of notations.}
\end{table}
